NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-03-20 Manuscript/manuscriptPS.tex
Update the table listing simulated systems

    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 & 0  & 120:24 & 5760 & 0  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
%    \hline
%    POPG/Na$^+$  & CHARMM36 \cite{??} \todoi{Correct citation for CHARMM POPG}        &0 & 0        & ? 			   		& ? & 0  & ?  & ? & ? & \cite{??}
%    \todoi{Details to be filled and data to be uploaded in Zenodo by Ollila.}  \\
%    POPG/Na$^+$  & Slipids \cite{jambeck13}     &0 & 0        & 288 			   		& 10664 & 0  & 298  & 250 & 100 & \cite{slipidsPOPGfiles} \\
%    \hline
%    DPPG/Na$^+$  & Slipids \cite{jambeck13}     &0 & 0        & 288 			   		& 11232 & 0  & 314  & 200 & 100 & \cite{slipidsDPPGfiles} \\
%    DPPG/Na$^+$  & Slipids \cite{jambeck13}     &0 & 0        & 288 			   		& 11232 & 0  & 298  & 400 & 100 & \cite{slipidsDPPGfilesT298K} \\

>>>>

    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{??}          &0 & 0 & 250:50 & ?     & 0  & 298  & 200 & ?   & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\
    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{??}          &0 & 0 & 110:22 & 4620  & 0  & 298  & 500 & 100 & \cite{charmm36pops+83popcT298Kpiggot}  \\
    POPC:POPS (5:1)/Na$^+$ & CHARMM36 \cite{??}          &0 & 0 & 110:22 & 4620  & 0  & 298  & 500 & 100 & \cite{charmm36pops+83popcT298KpiggotSODIUM}  \\
    POPC:POPS (1:1)/K$^+$  & CHARMM36 \cite{??}          &0 & 0 & 150:150 & ?    & 0  & 298  & 200 & ?   & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\
    POPC:POPS\todoi{This is also probably OPPS? These should be corrected in this table as well.} (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 & 0  & 120:24 & 5760 & 0  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)        & CHARMM36 \cite{??}\todoi{These are with NBFIX from Ref. \citenum{kim16}}          &0 & 150 \todoi{Concentration to be checked} & 250:50 & ?  & ?  & 298  & 200 & ?  & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\
    POPC:POPS (5:1)        & CHARMM36 \cite{??}\todoi{These are with NBFIX from Ref. \citenum{kim16}}          &0 & 1000 \todoi{Concentration to be checked} & 250:50 & ?  & ?  & 298  & 200 & ?  & \cite{??} \todoi{Trajectories and further details to be added by J. Madsen}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 &100 & 120:24 & 5760 & 10  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 &300 & 120:24 & 5760 & 31  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 &1000 & 120:24 & 5760 & 104  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0 &3000 & 120:24 & 5760 & 311  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
